\documentclass[a4paper,11pt]{article}

\usepackage{amsfonts,amsmath,amssymb,amscd,amstext}
\usepackage{theorem}

\renewcommand{\thepage}{} % astuce pour supprimer les numéros de pages

\addtolength{\textheight}{3 cm}
\addtolength{\topmargin}{-2cm}
\addtolength{\textwidth}{3cm}
\addtolength{\oddsidemargin}{-2.1cm}
\addtolength{\evensidemargin}{-2.1cm}
%\theoremstyle{definition}

\theorembodyfont{\rmfamily}
\newtheorem{exo}{Exercise}

\def\ch{\mathrm{ch}}
\def\sh{\mathrm{sh}}
\def\th{\mathrm{th}}

\newcommand{\exoskip}{\addvspace{15pt plus 2pt minus 3pt}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\eps}{\varepsilon}
\newcommand{\inter}{\stackrel{\circ}}
\newcommand{\fr}{\mathrm{Fr}}
\newcommand{\ds}{\displaystyle}
\newcommand{\E}{\mathrm{E}}

\begin{document}
{\large
\begin{center}{\bf Math 242 Final Exam, Friday 12 December}
\end{center}}
\vspace*{0.5cm}
\large{\textbf{Name:} \hfill \textbf{Last 4 digits of SSN:}}\hspace{2cm}
\vspace{1cm}

\noindent Show all \textbf{work clearly}, \textbf{make sentences}. No work means no credit. The points are:\\
ex1: 10, ex2: 10, ex3: 10, ex4: 15, ex5: 15, ex6: 15, ex7: 15, ex8: 10, ex9: 20, ex10: 15, ex11: 15 (Total=150 pts).
\vspace*{0.5cm}

\begin{exo}
\begin{enumerate}
\item We give a differential equation $y'=f(x,y)$. Write the algorithm of the Euler method. Apply this algorithm to find the first two ($y_0$ and $y_1$) value of an approximate solution of the differential equation 
\[ y'=3x+2y, \quad y(0)=1,\]
and with step size $h=0.5$.
\vspace*{6cm}
\item Method of variation of parameters in the case $n=2$:\\
We consider the second-order linear differential equation 
\[ y''+P(x)y'+Q(x)y=f(x) ,\]
where $P$, $Q$ and $f$ are continuous. A general solution is given by:
\[ y_c(x)=c_1 y_1(x)+c_2y_2(x) ,\]
where $c_1$ and $c_2$ are constants.\\
What will be the form of a particular solution ? To find this solution, what system of equations, with unknown $c_1'$ and $c_2'$, do we have to solve ?
\end{enumerate}
\end{exo}

\newpage

\begin{exo}
Solve the initial value problem:
\[ xy'=2y+x^3\cos x, \quad y(\pi)=1 .\]
\end{exo}
%18 p56 

\vspace*{12cm}

\begin{exo}
Find a general solution of the differential equation
\[ 3xy'=1+y^2 .\]
\end{exo}

\newpage

\begin{exo}
We consider the following differential equation:
\[ xy'+6y=3xy^{4/3}. \]
\begin{enumerate}
\item What kind of equation is it?
\vspace*{1cm}
\item What substitution do we have to do?
\vspace*{1cm}
\item What differential equation do we obtain after the substitution?
\vspace*{2cm}
\item Solve this last differential equation and then find the expression of $y$.
\end{enumerate}
\end{exo}

\vspace*{7cm}


\begin{exo}
Show that the differential equation
\[ \left(1+ye^{xy}\right)dx+(2y+xe^{xy})dy=0,\]
is exact and then solve it.
\end{exo}

\vspace*{7cm}

\begin{exo}
We give the differential equation:
\[ \frac{dx}{dt}=6x-2x^2 .\]
\begin{enumerate}
\item What are the critical points ? Use a phase diagram to determine whether each critical point is stable or unstable.
\vspace*{3cm}
\item Solve this differential equation with $x(0)=1$.
\end{enumerate}
\end{exo}

\newpage

\begin{exo}
Give the form of a particular solution in each case, but do not determine the values of the coefficients:
\begin{enumerate}
\item $y^{(114)}+59y'=x^3+46x-13$,
\vspace*{1cm}
\item $y^{(3)}+y''-y'-y=(x^2+1)e^{-x}$,
\vspace*{3cm}
\item $y^{(3)}+y''-y'-y=5e^{4x}(13x^2+101x-964)\cos(7x)$.
\end{enumerate}
\end{exo}

\vspace*{3cm}

\begin{exo}
Find the form of a solution of the following differential equation
\[ y^{(3)}-5y''+8y'-4y=0 .\]
\textit{Hint:} 1 is a root of the characteristic equation.
\end{exo}

\vspace*{5cm}

\begin{exo}
Solve the initial value problem without the Laplace transform:
\[ y''-6y'+8y=24xe^{-2x}, \quad y(0)=5/12,\ y'(0)=13/6.\]
\end{exo}

\vspace*{13cm}

\begin{exo}
$1)$ Find the Laplace transform of the following functions:
\[ f_1(t)=t\cos(2t), \quad f_2(t)=\frac{2\sin 3t}{t}.\]
We recall that $\lim_{x\to \infty} \arctan x=\pi/2$ and that $\int\frac{1}{a^2+x^2}dx=1/a \arctan(x/a)$.\\
$2)$ Find the inverse Laplace transform of:
\[  F(s)=\frac{s+6}{s^2-10s+41}.\]
\end{exo}

\newpage
\, \vspace*{3cm}

\begin{exo}
Solve the initial value problem using the Laplace transform:
\[ y''-5y'+6y=-3e^{2x}, \qquad y(0)=-1,\ y'(0)=2.\]
\end{exo}



\end{document}