\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amsfonts,amssymb,amsxtra}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}
\renewcommand{\theenumi}{(\alph{enumi})} 
\renewcommand{\labelenumi}{\theenumi}

\pagestyle{empty}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\textheight}{9.5in}

\theoremstyle{definition}
\newtheorem{problem}{Problem}

\begin{document}

\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Spring 2016}\hfill{\large\bf Page 1/3}\hrule

\bigskip
\begin{center}
  \begin{tabular}{|ll|}
    \hline & \cr
    {\bf Name: } & \makebox[12cm]{\hrulefill}\cr & \cr
    {\bf VIP ID:} & \makebox[12cm]{\hrulefill}\cr & \cr
    \hline
  \end{tabular}
\end{center}
\begin{itemize}
\item Write your name and VIP ID in the space provided above.
\item The test has three (3) pages, including this one.
\item Credit for each problem is given in parentheses at the right of the problem number.
\item No books, notes or scratch paper may be used on this test.
\item An approved calculator may be used on this test.
\end{itemize}
\hrule

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 2
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Spring 2016}\hfill{\large\bf Page 2/3}\hrule

\bigskip
\begin{problem}[10 + 15 pts]
Evaluate the following integrals.
\begin{enumerate}
\item $\displaystyle{\int_{0}^{4} \ln(y^2 + 1) \, dy} = $
\vspace{1cm}
\item $\displaystyle{\int_{10}^{103} (9x^2+4)e^{3x}\, dx = }$
\vspace{8cm}
\end{enumerate}
\end{problem}
\hrule

\begin{problem}[25 pts]
What is the average value of $f(x) = \displaystyle{\sqrt{\vphantom{\lvert} 9-x^2}}$ over the interval $0 \leq x \leq 3$?  Round your answer to two decimal places.
\end{problem}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 3
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Spring 2016}\hfill{\large\bf Page 3/3}\hrule

\bigskip
\begin{problem}[25 pts]
Find the consumer surplus for the demand curve $p=110-2q$ when $q=25$ items are sold.
\vspace{10cm}
\end{problem}
\hrule

\begin{problem}[25 pts]
The marginal cost of drilling an oil well depends on the depth at which you are drilling; drilling becomes more expensive, per meter, as you dig deeper into the earth.  The fixed costs are one million dollars and, if $x$ is the depth in meters, the marginal costs are $C'(x) = 500 + 12x$ dollars per meter.  Find the total cost of drilling a 400-meter well.
\end{problem}

\end{document}
