\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amsfonts,amssymb,amsxtra}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}
\renewcommand{\theenumi}{(\alph{enumi})} 
\renewcommand{\labelenumi}{\theenumi}

\pagestyle{empty}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\textheight}{9.5in}

\theoremstyle{definition}
\newtheorem{problem}{Problem}

\begin{document}

\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Spring 2016}\hfill{\large\bf Page 1/3}\hrule

\bigskip
\begin{center}
  \begin{tabular}{|ll|}
    \hline & \cr
    {\bf Name: } & \makebox[12cm]{\hrulefill}\cr & \cr
    {\bf VIP ID:} & \makebox[12cm]{\hrulefill}\cr & \cr
    \hline
  \end{tabular}
\end{center}
\begin{itemize}
\item Write your name and VIP ID in the space provided above.
\item The test has three (3) pages, including this one.
\item Credit for each problem is given in parentheses at the right of the problem number.
\item No books, notes or scratch paper may be used on this test.
\item An approved calculator may be used on this test.
\end{itemize}
\hrule

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 2
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Spring 2016}\hfill{\large\bf Page 2/3}\hrule

\bigskip
\begin{problem}[10 + 15 pts]
Evaluate the following integrals.
\begin{enumerate}
\item $\displaystyle{\int_{1.1}^{1.8} e^t \ln t\, dt} = $
\vspace{1cm}
\item $\displaystyle{\int_{1}^{108} (10x^2-3)e^{5x}\, dx = }$
\vspace{8cm}
\end{enumerate}
\end{problem}
\hrule

\begin{problem}[25 pts]
Find the average value of the function $f(x) = 11+10x-x^2$ between $x=0$ and $x=3$.
\end{problem}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 3
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Spring 2016}\hfill{\large\bf Page 3/3}\hrule

\bigskip
\begin{problem}[25 pts]
The demand curve for a product is given by $q=100-2p$ and the supply curve is given by $q=3p-60$.  Find the consumer surplus at the equilibrium.
\vspace{10cm}
\end{problem}
\hrule

\begin{problem}[25 pts]
The marginal cost function of producing $q$ mountain bikes is $C'(q) = \dfrac{600}{0.3q+5}$.  If the fixed cost in producing the bicycles is \$2000, find the total cost to produce 30 bicycles.
\end{problem}

\end{document}
