\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amsfonts,amssymb,amsxtra}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows, calc}
\renewcommand{\theenumi}{(\alph{enumi})} 
\renewcommand{\labelenumi}{\theenumi}

\pagestyle{empty}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\textheight}{9.5in}

\newtheorem{problem}{Problem}

\begin{document}

\noindent{\large\bf MATH 241}\hfill{\large\bf Exam\#3.}\hfill{\large\bf
  Spring 2014}\hfill{\large\bf Page 1/4}\hrule

\bigskip
\begin{center}
  \begin{tabular}{|ll|}
    \hline & \cr
    {\bf Name: } & \makebox[12cm]{\hrulefill}\cr & \cr
    {\bf 4-digit code:} & \makebox[12cm]{\hrulefill}\cr & \cr
    \hline
  \end{tabular}
\end{center}
\begin{itemize}
\item Write your name and the last 4 digits of your SSN in the space provided above.
\item The test has three (3) pages, including this one.
\item The test is fifty (50) minutes long.
\item Enter your answer in the box(es) provided.
\item You must show sufficient work to justify all answers unless
  otherwise stated in the problem.  Correct answers with inconsistent
  work may not be given credit.
\item Credit for each problem is given in parentheses at the right of
  the problem number.
\item No books, notes or calculators may be used on this test.
\end{itemize}
\hrule

\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
    &&\cr
    {\large\bf Page} & {\large\bf Max.~points} & {\large\bf Your points} \cr
    &&\cr
    \hline
    &&\cr
    {\Large 2} & \Large 50 & \cr
    &&\cr
    \hline
    &&\cr
    {\Large 3} & \Large 50 & \cr
    &&\cr
    \hline\hline
    &&\cr
    {\large\bf Total} & \Large 100 & \cr
    &&\cr
    \hline
  \end{tabular}
\end{center}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 2
\noindent{\large\bf MATH 241}\hfill{\large\bf Exam\#3.}\hfill{\large\bf
  Spring 2014}\hfill{\large\bf Page 2/4}\hrule

\bigskip
{\problem[25 pts] \em Calculate the double integral
$\displaystyle{\iint_R \frac{1+x^2}{1+y^2}}\, dA$, for the rectangle
$R=[0,1]\times[0,1]$.}
\vspace{8cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\hrule
{\problem[25 pts] \em Use a double integral to compute the volume under
the surface $z=xy$ and above the region bounded by $x=y^2$ and $x=y^3$.}
\vspace{8cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 3
\noindent{\large\bf MATH 241}\hfill{\large\bf Exam\#3.}\hfill{\large\bf
  Spring 2014}\hfill{\large\bf Page 3/4}\hrule

\bigskip
{\problem[25 pts] \em Evaluate $\displaystyle{\iint_R (3x+4y^2)\, dA}$,
where $R$ is the region in the upper half-plane bounded by the circles
$x^2+y^2=1$ and $x^2+y^2=4$.}
\vspace{8cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\hrule
{\problem[25 pts] \em A rectangular box without a lid is to be made from $12\,
\text{m}^2$ of cardboard.  We want to find the maximum volume of such a box.}

\noindent{\small We model the box to have length $x$, width $y$ and height $z$.  That way, the
volume can be expressed by the formula $V = xyz$.   We need to find the
maximum value of the function $V(x,y,z) = x y z$, with a constraint on the
variables: $xy + 2yz + 2zx = 12$.  Use Lagrange multipliers to solve this
problem.}

\vspace{7cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\end{document}
