\documentclass[12pt]{amsart}
\overfullrule = 0pt

\usepackage{amssymb,amsmath,amsthm,epsfig}
\usepackage{showkeys}

\pagestyle{empty}

\topmargin=-0.5in
\textwidth=6.5in
\textheight=9.0in
\oddsidemargin=0.0in
\evensidemargin=0.0in

\begin{document}
\thispagestyle{empty}
\begin{center}
\Large{\bf Elementary Differential Equations \\ Math 242}
\end{center}
\vspace*{0.8cm}
\large{{\bf Instructor:} Antoine Flattot, 777-5882, flattot@math.sc.edu}\\
\large{{\bf Lectures:} MWF 1:25PM - 2:15PM, LC 101}\\
\large{{\bf Office Hours:} MWF 11:15AM - 12:15AM, or by appointment, LC 400D}\\[0.8cm]
\noindent {\bf Overview:} Many of the principles, or laws, underlying the behavior of the natural world
are statements or relations involving rates at which things happen. When expressed in mathematical
terms, the relations are equations and the rates are derivatives. Equations containing derivatives are
called differential equations. Therefore, to understand and to investigate problems involving the 
motion of fluids, the flow of current in electric circuits, the dissipation of heat in solid objects,
the propagation and detection of seismic waves, the change of populations, it is necessary to 
be able to solve or study differential equations.\\[0.3cm] 
\noindent {\bf Instructional Objectives:} We will cover as much as possible of the following topics:\\
\hspace*{0.3cm} (1) First order differential equations.\\
\hspace*{0.3cm} (2) Numerical solutions of differential equations.\\
\hspace*{0.3cm} (3) Higher order linear differential equations.\\
\hspace*{0.3cm} (4) The Laplace transform.\\
\hspace*{0.3cm} (5) Systems of differential equations.\\[0.3cm]
\noindent {\bf Textbook:} {\em Differential Equations, computing and modeling}, by Edwards and Penney,
Fourth Edition.\\[0.3cm]
{\bf Prerequisite:} Completion of Math 142 with a grade of C or better, or qualification by placement.\\[0.3cm]
{\bf Grading:} Your grade in this course will be based on your performance on  quizzes, Homeworks, three midterms 
exams and a final exam. The weights assigned to each of these components will be:
\[
\begin{array} {ll}
\mbox{ Homeworks } & 20 \% \\
\mbox{ Three midterm exams } & 20 \% \mbox{ each} \\
\mbox{ Final exam } & 20 \%
\end{array}
\]
Course grades will be determined according to the scale:\\
A 90-100, B+ 85-89, B 80-84, C+ 75-79, C 70-74, D+ 65-69, D 60-64 F 0-59.\\[0.3cm]
{\bf Exams:} {\em Tentative} dates and topics for these exams are:
\[
\begin{array}{lll}
\mbox{ Exam 1 } & \mbox{ Wednesday, September 19} & \mbox{ Chapter } 1 \\
\mbox{ Exam 2 } & \mbox{ Wednesday, October 31} & \mbox{ Chapters 2 \& 3}\\
\mbox{ Exam 3 } & \mbox{ Monday, November 26} & \mbox{ Chapter } 7\\
\mbox{ Final} & \mbox{ Friday, December 14, 2:00PM}  & \mbox{ Comprehensive}
\end{array}
\]
Thursday October 4 is the last day to drop a course or withdraw without a grade of ``WF'' being recorded.
There will be no make-up exams. In case that you miss an exam because of  documented reasons of illness, family
emergency, or participation in a University sponsored event, if you have contact me immediately and provide me 
with the documentation, then the grade of the missed exam will be substituted by the grade of the final 
exam.\\[0.3cm]
{\bf Homeworks:} A homework assignment (of approximately 1 or 2
problems) will be assigned at each class and it will be collected at the next class. 
There will be  no make-up homeworks. In case that you are unable to attend the class,
during the day that you turn in homework, because of a documented
reason of illness, family emergency or of participation in a University
sponsored event, if you have contact me immediately and provide me with the
documentation, then the grade of your missed homework will be dropped.\\[0.3cm]
{\bf Attendance:} Regular class attendance is important. Consistent
with the USC Undergraduate Bulletin, a grade penalty may be applied to
any student missing more than 4 classes.\\[0.3cm]
{\bf Academic Honesty:} Cheating and plagiarism will not be tolerated
in this course. You may discuss homework problems with others, but do
not copy solutions from another student or from a book. Violations of
this policy will be dealt with a matter consistent with University
regulations. \\[0.3cm]
{\bf Cell phone policy:} Turn off cell phones during class and exam period.

\end{document}
 