\documentclass[a4paper,11pt]{article}

\usepackage{amsfonts,amsmath,amssymb,amscd,amstext}
\usepackage{theorem}

\renewcommand{\thepage}{} % astuce pour supprimer les numéros de pages

\addtolength{\textheight}{3 cm}
\addtolength{\topmargin}{-2cm}
\addtolength{\textwidth}{3cm}
\addtolength{\oddsidemargin}{-2.1cm}
\addtolength{\evensidemargin}{-2.1cm}
%\theoremstyle{definition}

\theorembodyfont{\rmfamily}
\newtheorem{exo}{Exercise}

\def\ch{\mathrm{ch}}
\def\sh{\mathrm{sh}}
\def\th{\mathrm{th}}

\newcommand{\exoskip}{\addvspace{15pt plus 2pt minus 3pt}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\eps}{\varepsilon}
\newcommand{\inter}{\stackrel{\circ}}
\newcommand{\fr}{\mathrm{Fr}}
\newcommand{\ds}{\displaystyle}
\newcommand{\E}{\mathrm{E}}

\begin{document}
{\large
\begin{center}{\bf Math 242 Test 2, Friday 2 November}
\end{center}}
\vspace*{0.5cm}
\large{\textbf{Name:} \hfill \textbf{Last 4 digits of SSN:}}\hspace{2cm}
\vspace{1cm}

\noindent Show all work clearly, make sentences. No work means no credit. The points are:\\
ex1: 10, ex2: 20, ex3: 25, ex4: 15, ex5: 15 and the course questions are over 15 points.
\vspace*{1cm}

\textbf{\large Course Questions}
\begin{enumerate}
\item Write the logistic equation and precise what is the carrying capacity. What tool do you use to solve this kind of differential equation ?
\vspace*{4cm}
\item For what kind of differential equation do we speak about critical point ? Then give the definition of this point and precise what is an equilibrium solution.
\vspace*{4cm}
\item For a second-order linear differential equation with constant coefficients, give the characteristic equation and the form of solutions depending on the roots of this equation (give the three cases).
\vspace*{3cm}
\end{enumerate}

\newpage

\begin{exo}
We give the differential equation:
\[ \frac{dx}{dt}=3x-x^2 .\]
Find the critical points of this equation and use a phase diagram to determine wether each critical point is stable or unstable.
\end{exo}

\vspace*{5cm}

\begin{exo}
We give an initial value problem and its exact solution $y(x)$:
\[ y'=4x-2y, \quad y(0)=1, \quad y(x)=2e^{-2x}+2x-1. \]
Apply Euler's method to approximate the solution on the interval $[0,1]$ with step size $h=0.25$. Write the formula you use for the computation. Then compare the four-decimal-place values of the approximate solution with the values of the exact solution using the following array. Does this step size look good ?
\vspace*{6cm}
{\renewcommand{\arraystretch}{1.5}
\[ \begin{array}{|r|c|c|c|c|c|}
      \hline \mbox{x} & 0 & 0.25 & 0.5 & 0.75 & 1 \\
      \hline \mbox{approx solution} & \hspace*{2cm} & \hspace*{2cm} & \hspace*{2cm} & \hspace*{2cm} & \hspace*{2cm} \\
      \hline \mbox{exact solution} & \hspace*{2cm} & \hspace*{2cm} & \hspace*{2cm} & \hspace*{2cm} & \hspace*{2cm} \\
      \hline
    \end{array} \]}
\end{exo}
%2.4.4
\vspace*{1cm}

\begin{exo}
Solve the differential equation:
\[ y^{(3)}-9y''+24y'-16y=0.\]
You will first find a small integral root of the characteristic equation by inspection.\\
Then find the unique solution satisfying the initial conditions:
\[ y(0)=1, \ y'(0)=2, \ y''(0)=0.\]
\end{exo}

\vspace*{10cm}

\begin{exo}
Solve the initial value problem:
\[ y''-4y'+5y=0, \quad y(0)=2, \ y'(0)=1.\]
\end{exo}

\newpage

\begin{exo}
Find a linear homogeneous constant-coefficient equation with the general solution:
\[ y(x)= Ae^{-2x}+B\cos(4x)+ C\sin(4x)+x(D\cos(4x)+E\sin(4x)) .\]
\end{exo}


\end{document}