\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amsfonts,amssymb,amsxtra}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}
\renewcommand{\theenumi}{(\alph{enumi})} 
\renewcommand{\labelenumi}{\theenumi}

\pagestyle{empty}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\textheight}{9.5in}

\newtheorem{problem}{Problem}

\begin{document}

\noindent{\large\bf MATH 141}\hfill{\large\bf Exam\#3.}\hfill{\large\bf
  Spring 2013}\hfill{\large\bf Page 1/5}\hrule

\bigskip
\begin{center}
  \begin{tabular}{|ll|}
    \hline & \cr
    {\bf Name: } & \makebox[12cm]{\hrulefill}\cr & \cr
    {\bf 4-digit code:} & \makebox[12cm]{\hrulefill}\cr & \cr
    \hline
  \end{tabular}
\end{center}
\begin{itemize}
\item Write your name and the last 4 digits of your SSN in the space provided above.
\item The test has five (5) pages, including this one.
\item You have fifty (50) minutes to complete the exam.
\item Enter your answer in the box(es) provided.
\item You must show sufficient work to justify all answers unless
  otherwise stated in the problem.  Correct answers with inconsistent
  work may not be given credit.
\item Credit for each problem is given in parentheses at the right of
  the problem number.
\item No books, notes or calculators may be used on this test.
\end{itemize}
\hrule

\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
    &&\cr
    {\large\bf Page} & {\large\bf Max.~points} & {\large\bf Your points} \cr
    &&\cr
    \hline
    &&\cr
    {\Large 2} & \Large 30 & \cr
    &&\cr
    \hline
    &&\cr
    {\Large 3} & \Large 20 & \cr
    &&\cr
    \hline
    &&\cr
    {\Large 4} & \Large 20 & \cr
    &&\cr
    \hline
    &&\cr
    {\Large 5} & \Large 30 & \cr
    &&\cr
   \hline\hline
    &&\cr
    {\large\bf Total} & \Large 100 & \cr
    &&\cr
    \hline
  \end{tabular}
\end{center}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 1
\noindent{\large\bf MATH 141}\hfill{\large\bf Exam\#3.}\hfill{\large\bf
  Spring 2013}\hfill{\large\bf Page 2/5}\hrule

\bigskip
{\problem[30 pts] \em Sketch the graph of the function}
\begin{equation*}
f(x) = \frac{x}{x-2}
\end{equation*}
Make sure to indicate clearly:
\begin{itemize}
\item Zeros of the function.
\item Domain.
\item Vertical and horizontal asymptotes.
\item Extreme values and inflection points.
\item Intervals of increase/decrease.
\item Intervals of concavity.
\end{itemize}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 2
\noindent{\large\bf MATH 141}\hfill{\large\bf Exam\#3.}\hfill{\large\bf
  Spring 2013}\hfill{\large\bf Page 3/5}\hrule

\bigskip
{\problem[20 pts] \em An oil refinery is located on the north bank of a
straight river that is 6~km wide.  A pipeline is to be constructed from
the refinery to storage tanks located on the south bank of the river 8
km east of the refinery.  The cost of laying pipe is \$1,000/km over
land to a point $P$ on the north bank, and \$3,000/km under the river
to the tanks.  To minimize the cost of the pipeline, where should $P$ be
located?}

\noindent{\textbf{Hints:} Use ``thousands of dollars" as your monetary units
for simplicity. Use the approximations $\sqrt{40} \approx 6.32$,
$3\sqrt{40} \approx 18.97$ if needed.}
\vspace{18cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (0cm,0cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 3
\noindent{\large\bf MATH 141}\hfill{\large\bf Exam\#3.}\hfill{\large\bf
  Spring 2013}\hfill{\large\bf Page 4/5}\hrule

\bigskip
{\problem[20 pts] \em A rectangular storage container with an open top
is to have a volume of 20\,m$^3$.  The length of its base is twice the
width.  Material for the base costs \$10 per square meter.  Material for
the sides costs \$6 per square meter.  Find the cost of materials for
the cheapest such container.}
\vspace{18cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (0cm,0cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\newpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 4
\noindent{\large\bf MATH 141}\hfill{\large\bf Exam\#3.}\hfill{\large\bf
  Spring 2013}\hfill{\large\bf Page 5/5}\hrule

\bigskip
{\problem[10 pts] \em Does there exist a function $f$ such that $f(0)=-1,
f(2)=4$, and $f'(x)\leq 2$ for all $x$?  Use the Mean Value Theorem to
either explain the function does not exist, or to build one that
satisfies those properties.}
\vspace{8cm}
\hrule
{\problem[20 pts] \em A ladder 10\,ft long rests against a vertical wall.  If
the bottom of the ladder slides away from the wall at a rate of 1\,ft/s,
how fast is the top of the ladder sliding down the wall when the bottom
of the ladder is 6~ft from the wall?}
\vspace{10cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (0cm,0cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}

\end{document}
