\documentclass[12pt]{amsart}
\usepackage{pgf,tikz}

\renewcommand{\theenumi}{(\roman{enumi})} 
\renewcommand{\labelenumi}{\theenumi}
\def\field#1{\mathbb{#1}}
\def\abs#1{\lvert {#1} \rvert}
\def\Lpnorm#1#2{\lVert {#1} \rVert_{#2}}
\theoremstyle{definition}
\newtheorem{problem}{Problem}
\theoremstyle{remark}
\newtheorem*{solution}{Solution}

\begin{document}
\title{Absolute Continuity}
\maketitle

\begin{problem}[\textcolor{red}{Spring'96}, \textcolor{red}{Spring'07}]
  Let $f\colon [0,1] \to \field{R}$.
  \begin{enumerate}
  \item Let $V_f(0,x)$ be the total variation of $f$ on $[0,x]$. Prove
    that if $f$ is absolutely continuous on $[0,1]$, so is $V_f(0,x)$.
  \item Define what it means for $f$ to be absolutely continuous.
  \end{enumerate}
\end{problem}
\begin{problem}[\textcolor{red}{Spring'05}]
  Let $\{ f_n \} \in AC(I)$, $I = [a,b]$. Assume that $f_n \to f
  (L_1)$ and $\{ f'_n\}$ is Cauchy ($L_1$).  Show that there exists $g
  \in AC(I)$ such that $f(x) = g(x)$~a.e.~$x \in I$.
\end{problem}
\begin{problem}[\textcolor{red}{Spring'05}]
  Let $f\colon I \to \field{R}$, $I = [a,b]$, and let $M \in
  \field{N}$.  Show that the following two statements are equivalent.
  \begin{enumerate}
  \item $f \in AC(I)$.
  \item For every $\varepsilon >0$ there exists $\delta =
    \delta(\varepsilon) > 0$ such that for every collection of
    intervals $\{ J_k = [a_n, b_n] \subset I \}$ with $\sum_n
    \xi_{J_n}(x) \leq M$ and $\sum_n \abs{J_n} \leq \delta$, we have
    $\sum_n \abs{ f(b_n) - f(a_n) } \leq \varepsilon$.
  \end{enumerate}
\end{problem}
\begin{problem}[\textcolor{red}{Fall'05}]
  Suppose $f$ is absolutely continuous on $[0,1]$.  Prove that so is
  $e^f$.
\end{problem}
\begin{problem}[\textcolor{red}{Spring'06}]
  Let
  \begin{equation*}
    f(x) = \begin{cases} 
      x^p \sin (x^{-q}) &\text{if } 0 < x\leq 1\\
      0 &\text{if }x=0.
    \end{cases}
  \end{equation*}
  \begin{enumerate}
  \item Show that if $0<q<p$, then $f$ is absolutely continuous.
  \item However, if $0<p\leq q$, show that $f$ is not of bounded
  variation.
  \end{enumerate}
\end{problem}
\begin{problem}[\textcolor{red}{Spring'06}]
  Let $f_n\colon [0,1] \to [-1,1]$, $n \in \field{N}$ be a sequence of
  absolutely continuous functions.  Suppose that $f_n \to f$
  uniformly.  Is $f$ absolutely continuous?
\end{problem}
\begin{problem}[\textcolor{red}{Fall'06}]
  Suppose that $f_n(x)$ is a sequence of increasing (in $x$),
  absolutely continuous functions on $[0,1]$ for which $f_n(0)=0$ for
  all $n$. Let
  \begin{equation*}
    g(x) = \sum_{n=1}^\infty f_n(x).
  \end{equation*}
  Prove that if $g(1)<\infty$, then $g$ is absolutely continuous on
  $[0,1]$.
\end{problem}
\end{document}
