\documentclass[12pt]{amsart}
\usepackage{pgf,tikz}

\renewcommand{\theenumi}{(\roman{enumi})} 
\renewcommand{\labelenumi}{\theenumi}
\def\field#1{\mathbb{#1}}
\def\abs#1{\lvert {#1} \rvert}
\theoremstyle{definition}
\newtheorem{problem}{Problem}
\theoremstyle{remark}
\newtheorem*{solution}{Solution}

\begin{document}
\title{Measurable Functions}
\maketitle

\section{one-liners}
\begin{problem}
  \textcolor{blue}{Suppose $\{ f > \lambda \}$ is measurable for each
    rational number $\lambda$. Is $f$ measurable?}
\end{problem}
\begin{problem}
  \textcolor{gray}{Let $(X,\mathcal{F},\mu)$ be a measure space.
    Suppose $f$ is a measurable real-valued function defined on
    $\field{R}$, and put $g(x) = 0$ if $f(x)$ is rational, and $g(x) =
    1$ if $f(x)$ is irrational.  Is $g$ measurable?}
\end{problem}
\begin{problem}
  \textcolor{gray}{Let $(X, \mathcal{F}, \mu)$ be a measure space.
    Suppose $f$ is measurable and $B \in \mathcal{B}_1$ is a Borel
    subset of $\field{R}$. Does it then follow that $f^{-1}(B) \in
    \mathcal{F}$?}
\end{problem}
\begin{problem}
  \textcolor{blue}{Suppose $f$ is a measurable real-valued function
    defined on $\field{R}$, and let $\phi$ be a real-valued
    Borel-measurable function defined on $\field{R}$.  Show that the
    composition $\phi \circ f$ is measurable.}
\end{problem}
\begin{problem}
  Suppose $f$ is measurable and show that for each reals $r,s > 0$,
  the truncations $f_{r,s}$ are measurable:
  \begin{equation*}
    f_{r,s} (x) = \begin{cases}
      r &\text{if } f(x) > r, \\
      f(x) &\text{if } -s \leq f(x) \leq r, \\
      -s &\text{if } f(x) < -s.
    \end{cases}
  \end{equation*}
\end{problem}
\begin{problem}
  Let $\{ f_n \}$ be a sequence of measurable functions defined on
  $\field{R}$, and let $A = \{ x \in \field{R} : \lim_n f_n(x) \text{
  exists} \}$.  Show that $A$ is measurable.
\end{problem}
\begin{problem}
  \textcolor{blue}{ Let $m(X)<\infty$, let $\lambda_n > 0$, $n \in
  \field{N}$, and suppose $\{ f_n \}$ is a sequence of extended
  real-valued measurable functions defined on $X$ that satisfies
  $\sum_{n=1}^\infty m\{ \abs{f_n} > \lambda_n \} < \infty$.  Prove
  that $\limsup_n \abs{f_n}/\lambda_n \leq 1$~a.e.}
\end{problem}
\begin{problem}[\textbf{NEW!}]
  Suppose that $f$ is Lebesgue measurable and $\phi$ is real-valued
  continuous and has the following property: For any null set $N$,
  $\phi^{-1}(N) \in \mathcal{L}$.  Show that $f \circ \phi$ is
  Lebesgue measurable.
\end{problem}

\section{Advanced Problems}
\begin{problem}
  Show that if $f$ is an everywhere finite real-valued measurable
  function, then it is the uniform limit of a sequence of elementary
  functions\footnote{ An \emph{elementary function} is one which
  assumes at most countably many values.} Also, unless $f$ is bounded,
  it is not the uniform limit of a sequence of simple functions.
\end{problem}
\begin{problem}
  \textcolor{blue}{ Suppose $(X, \field{F}, \mu)$ is a $\sigma$-finite
  measure space and let $f$ be a measurable function defined on
  $X$. Show that the function $\mu\{ \abs{f} > \lambda \}$, $\lambda
  >0$, is non-increasing and right-continuous.  Furthermore, if $f$,
  $f_1$ and $f_2$ are non-negative and measurable, and $\eta_1$,
  $\eta_2$ are non-negative real numbers so that $f \leq \eta_1 f_1 +
  \eta_2 f_2$ $\mu$-a.e., then for any $\lambda > 0$,}
  \begin{equation*}
    \textcolor{blue}{ \mu \{ f > (\eta_1 + \eta_2)\lambda \} \leq \mu
    \{ f_1 > \lambda \} + \mu \{ f_2 > \lambda \}.}
  \end{equation*}
\end{problem}
\begin{problem}
  \textcolor{blue}{ Show that if $\{ f_n \}$ is a sequence of
    measurable functions such that $\{ \abs{ f_n} \}$ is nondecreasing
    and $f = \lim_n f_n$, then $\lim_n \mu \{ \abs{f_n} > \lambda \} =
    \mu \{ \abs{f} > \lambda \}$ for any $\lambda > 0$.}
\end{problem}
\begin{problem}
  Let $f$ be a real-valued function defined on $[0,1]$ such that $f'$
  exists for all $x \in (0,1)$.  Prove that $f'$ is measurable.
\end{problem}
\begin{problem}
  Suppose $\{ A_n \}$ is a sequence of Lebesgue-measurable subsets of
  $\field{R}$, and let $f_n = \chi_{A_n}$, $n \in \field{N}$.  Find a
  necessary and sufficient condition for the sequence $\{ f_n \}$ to:
  \begin{enumerate}
  \item converge a.e.
  \item converge uniformly.
  \end{enumerate}
\end{problem}
\begin{problem}
  \textcolor{blue}{Show that if $f$ is a real-valued measurable
  function, then there exists a sequence $\{ \lambda_n \}$ of real
  numbers and a sequence $\{ A_n \}$ of measurable sets such that $f =
  \sum_{n=1} ^\infty \lambda_n \chi_{A_n}$ a.e.}
\end{problem}
\begin{problem}
  By means of an example, show that the conclusion of Egorov's Theorem
  does not necessarily hold if the $f_n$'s are not Lebesgue
  measurable.
\end{problem}
\begin{problem}
  Let $\{ f_m\}$ be a sequence of Lebesgue-measurable functions
  defined on $I=[a,b]$ and suppose that $\lim_n f_n = f$ exists
  a.e.~on $I$.  If $f \neq 0$ a.e.~and $f_n \neq 0$ a.e.~on $I$, prove
  that given $\varepsilon > 0$, there exists $c>0$ and a sequence $\{
  E_n \}$ of measurable subsets of $I$ such that $\abs{ f_n (x) } \geq
  c$, $x \in E_n$ and $\abs{ I \setminus E_n } \leq \varepsilon$ for
  $n \in \field{N}$.
\end{problem}


\section{Qual problems}
\begin{problem}[\textcolor{red}{August'99}]
  Suppose that $f$ is Lebesgue measurable and $0 \leq f(x) \leq 1$ on
  $[0,1]$, and let $\lambda(y) = m\{ x \in [0,1] : f(x) > y \}$, $y
  \geq 0$, where $m$ denotes Lebesgue measure. Show that $\lambda$ is
  non-increasing and continuous from the right on $[0,\infty)$.
\end{problem}
\begin{problem}[\textcolor{gray!65!red}{January'00}]
  \textcolor{gray}{Suppose $f_n$ are measurable functions on some
    measure space $(\Omega, \mathcal{A}, \mu)$, $n \in \field{N}$,
    and}
  \begin{equation*}
    \textcolor{gray}{ \sum_{n=1}^\infty \mu\{ x \in \Omega :
    \abs{f_n(x)} > 1/n \} < \infty.}
  \end{equation*}
  \textcolor{gray}{Prove that $f_n \to 0$~a.e.}
\end{problem}
\begin{problem}[\textcolor{gray!65!red}{August'00}]
  \textcolor{gray}{ Let $(X, \mathcal{F}, \mu)$ be a measure space and
    suppose $\{ f_n \}$ is a sequence of measurable functions with the
    property that for all $n \geq 1$,}
  \begin{equation*}
    \textcolor{gray}{ \mu \{ x \in X : \abs{f_n(x)} \geq \lambda \}
    \leq Ce^{-\lambda^2/n} }
  \end{equation*}
  \textcolor{gray}{for all $\lambda > 0$. (Here $C$ is a constant
    independent of $n$.)  Prove that}
  \begin{equation*}
    \textcolor{gray}{\limsup_n \frac{f_{2^n}}{\sqrt{2^n \log\big( \log
    (2^n)\big)}} \leq 1,~\text{a.e.}}
  \end{equation*}
\end{problem}
\begin{problem}[\textcolor{gray!65!red}{August'00}]
  \textcolor{gray}{ Answer the following questions:
    \begin{enumerate}
    \item Let $(X, \mathcal{F}, \mu)$ be a finite measure space.  Let
      $\{ f_n \}$ be a sequence of measurable functions.  Prove that
      $f_n \to f$ in measure if and only if every subsequence $\{
      f_{n_k} \}$ contains a further sequence $\{ f_{n_{k_j}} \}$ that
      converges almost everywhere to $f$.
    \item Let $(X, \mathcal{F}, \mu)$ be a finite measure space.  Let
      $F \colon \field{R} \to \field{R}$ be continuous and $f_n \to f$
      in measure.  Prove that $F(f_n) \to F(f)$ in measure.
    \end{enumerate}}
\end{problem}
\begin{problem}[\textcolor{red}{August'03}]
  Let $f$ be a bounded Lebesgue measurable function on $\field{R}$.
  Put
  \begin{equation*}
    g(x) = \sup \big\{ a \in \field{R} : \abs{ \{ y : y \in (x,x+1)
    \text{ and } f(y) > a \} } > 0 \big\},
  \end{equation*}
  where $\abs{\cdot}$ is the Lebesgue measure.  Prove $\liminf_{x\to
    0} g(x) \geq g(0)$.
\end{problem}
\begin{problem}[\textcolor{red}{January'99, August'06}]
  \textcolor{blue}{Let $f_n \colon \field{R} \to (-\infty, \infty]$,
    $n \in \field{N}$, be a sequence of Lebesgue measurable
    functions.}
  \begin{enumerate}
  \item \textcolor{blue}{Prove that $g(x) = \sup_n f_n(x)$ is Lebesgue
      measurable.}
  \item \textcolor{blue}{Prove that $h(x) = \limsup_n f_n(x)$ is
      Lebesgue measurable.}
  \end{enumerate}
\end{problem}

\end{document}
