\documentclass[a4paper,11pt]{article}

\usepackage{amsfonts,amsmath,amssymb,amscd,amstext}
\usepackage{theorem}

\renewcommand{\thepage}{} % astuce pour supprimer les numéros de pages

\addtolength{\textheight}{3 cm}
\addtolength{\topmargin}{-2cm}
\addtolength{\textwidth}{3cm}
\addtolength{\oddsidemargin}{-2.1cm}
\addtolength{\evensidemargin}{-2.1cm}
%\theoremstyle{definition}

\theorembodyfont{\rmfamily}
\newtheorem{exo}{Exercise}

\def\ch{\mathrm{ch}}
\def\sh{\mathrm{sh}}
\def\th{\mathrm{th}}

\newcommand{\exoskip}{\addvspace{15pt plus 2pt minus 3pt}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\eps}{\varepsilon}
\newcommand{\inter}{\stackrel{\circ}}
\newcommand{\fr}{\mathrm{Fr}}
\newcommand{\ds}{\displaystyle}
\newcommand{\E}{\mathrm{E}}

\begin{document}
{\large
\begin{center}{\bf Math 242 Final Exam, Saturday 3 May}
\end{center}}
\vspace*{0.5cm}
\large{\textbf{Name:} \hfill \textbf{Last 4 digits of SSN:}}\hspace{2cm}
\vspace{1cm}

\noindent Show all \textbf{work clearly}, \textbf{make sentences}. No work means no credit. The points are:\\
ex1: 7, ex2: 7, ex3: 11, ex4: 11, ex5: 10, ex6: 15, ex7: 10, ex8: 9, ex9: 15, ex10: 15, ex11: 15 (Total=125 pts).
\vspace*{0.5cm}

\begin{exo}
Solve the initial value problem:
\[ xy'+3y=3x^{-\frac{3}{2}}, \quad y(1)=0 .\]
\end{exo}
%22 p56 

\vspace*{8cm}

\begin{exo}
Find a general solution of the differential equation
\[ y'=1+x+y+xy .\]
\end{exo}

\newpage

\begin{exo}
We considere the following differential equation:
\[ xy'=6y+12x^4y^{2/3}. \]
\begin{enumerate}
\item What kind of equation is it?
\vspace*{1cm}
\item What substitution do we have to do?
\vspace*{1cm}
\item What differential equation do we obtain after the substitution?
\vspace*{2cm}
\item Solve this last differential equation and then find the expression of $y$.
\end{enumerate}
\end{exo}

\vspace*{6cm}

\begin{exo}
We consider the following differential equation:
\[ y'=\frac{-3x^2+4y^2}{4xy} .\]
\begin{enumerate}
\item Write this differential equation as a homogeneous one.
\vspace*{1.5cm}
\item Then solve this differential equation.
\end{enumerate}
\end{exo}

\newpage

\begin{exo}
Show that the differential equation
\[ \left(1+ye^{xy}\right)dx+(2y+xe^{xy})dy=0,\]
is exact and then solve it.
\end{exo}

\vspace*{9cm}

\begin{exo}
We give the differential equation:
\[ \frac{dx}{dt}=x^2+5x+6 .\]
\begin{enumerate}
\item What are the critical points ? Use a phase diagram to determine whether each critical point is stable or unstable.
\vspace*{3cm}
\item Solve this differential equation with $x(0)=-4$.
\end{enumerate}
\end{exo}

\newpage

\begin{exo}
Solve the differential equation
\[ y^{(3)}-6y''+9y'-54y=0,\]
using the fact that the function $x\mapsto e^{6x}$ is solution of this differential equation.\\
Then find the unique solution satisfying the initial conditions:
\[ y(0)=0, \ y'(0)=3, \ y''(0)=90.\]
\end{exo}

\vspace*{13cm}

\begin{exo}
Give the form of a particular solution in each case, but do not determine the values of the coefficients:
\begin{enumerate}
\item $y^{(114)}+59y'=x^4+x^3+x$,
\item $y^{(3)}+y''-y'-y=(x^2-2)e^{-x}$,
\item $y^{(3)}+y''-y'-y=5e^{4x}(x^2+5x-8)\cos(7x)$.
\end{enumerate}
\end{exo}

\newpage

\begin{exo}
Solve the initial value problem without the Laplace transform:
\[ y''-2y'+10y=9xe^{x}, \quad y(0)=2,\ y'(0)=0.\]
\end{exo}

\vspace*{13cm}

\begin{exo}
$1)$ Find the Laplace transform of the following functions:
\[ f_1(t)=t\sin(2t), \quad f_2(t)=\frac{\sin t}{t}.\]
We recall that $\lim_{x\to \infty} \arctan x=\pi/2$.\\
$2)$ Find the inverse Laplace transform of:
\[  F_1(s)=\frac{s+6}{s^2+4s+8},\quad   F_2(s)=\ln\left(\frac{s^2+1}{s^2+4}\right).\]
\end{exo}

\newpage
\vspace*{4cm}

\begin{exo}
Solve the initial value problem using the Laplace transform:
\[ x^{(3)}-x''-8x'+12x=0, \qquad x(0)=-3,\ x'(0)=22\ \mbox{and}\ x''(0)=-25.\]
\textit{Hint:} $2$ is a root of the characteristic equation.
\end{exo}

%\begin{exo}
%Solve the initial value problem using the Laplace transform:
%\[ x''-6x'+8x=8, \qquad x(0)=x'(0)=0 .\]
%\end{exo}

\end{document}