\documentclass[12pt]{amsart}

\renewcommand{\theenumi}{(\alph{enumi})} 
\renewcommand{\labelenumi}{\theenumi}

\pagestyle{empty}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\textheight}{9.5in}

\newtheorem{problem}{Problem}

\begin{document}
\noindent{\large\bf MATH 141}\hfill{\large\bf HW Feb 26}\hfill{\large\bf
  Spring 2010}\hfill{\large\bf (due Mar 2)}\hrule

\bigskip
{\problem An open box is to be made from a 16-inch by 30-inch piece of
  card-board by cutting out squares of equal size from the four
  corners and bending up the sides.  What size should the squares be
  to obtain a box with the largest volume?} 

{\problem A garden is to be laid out in a rectangular area and
  protected by a chicken wire fence. What is the largest possible area
  of the garden if only 100 running feet of chicken wire is available
  for the fence?}

{\problem A rectangular field is to be bounded by a fence on three
  sides and by a straight stream on the fourth side.  Find the
  dimensions of the field with maximum area that can be enclosed using
  1000 ft of fence.}

{\problem A rectangular plot of land is to be fenced in using two
  kinds of fencing.  Two opposite sides will use heavy-duty fencing
  selling for \$3 a foot, while the remaining two sides will use
  standard fencing selling for \$2 a foot.  What are the dimensions of
  the rectangular plot of greatest area that can be fenced in at a
  cost of \$6000?}

{\problem Find the dimensions of the rectangle with maximum area that
  can be inscribed in a circle of radius 10.}

{\problem A container with square base, vertical sides, and an open
  top is to be made from 1000~ft$^2$ of material.  Find the dimensions
  of the container with greatest volume.}

{\problem A box with square base is taller than it is wide.  In order
  to send the box through the U.S.~mail, the height of the box and the
  perimeter of the base can sum to no more than 108 in.  What is the
  maximum volume for such a box?}

{\problem A church window consisting on a rectangle topped by a
  semicircle is to have a perimeter $p$.  Find the radius of the
  semicircle if the area of the window is to be maximum.}

{\problem An offshore oil well is located at a point $W$ that is 5~km
  from the closest point $A$ on a straight shoreline.  Oil is to be
  piped from $W$ to a shore point $B$ that is 8~km from $A$ by piping
  it on a straight line under water from $W$ to some shore point $P$
  between $A$ and $B$, and then on to $B$ via pipe along the
  shoreline.  If the cost of laying pipe is \$1,000,000/km under water
  and \$500,000/km over land, where should the point $P$ be located to
  minimize the cost of laying the pipe?} 

{\problem Find the radius and height of the right circular cylinder of
  largest volume that can be inscribed in a right circular cone with
  radius 5 inches and height 10 inches.}

\end{document}
