\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage{nopageno}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{gensymb}
\pagestyle{fancy}

\newcommand{\blank}[1]{\rule[-1pt]{#1}{.5pt}}

\pdfpagewidth 8.5in
\pdfpageheight 11in

\title{Algebra/Trig Warm-up}

\lhead[Page \thepage]{Algebra/Trig Warm-up}
\rhead[Algebra/Trig Warm-up]{}
\chead{}

\fancyfoot{}

\begin{document}
\noindent Name \blank{3in}\\

Directions: Read each question carefully and answer in the space provided. 

\begin{enumerate}
\vskip .05in
\item
Solve for $x$. Check your solution(s). $$\dfrac{x - 2}{x + 6} = \dfrac{x + 1}{x - 3}$$

\vskip 2.75in
\item
Solve for $x$. Check your solution(s). $$\sqrt{x} - \sqrt{x - 9} = 1$$

\eject
\item
Solve the inequality. Give your answer in interval notation. $$5 | x - 2 | + 3 > 4$$

\vskip 3.25in
\item
Determine the center and the radius of the circle and sketch the graph. $$x^2 + 6x + y^2 - 4y = 12$$

\eject
\item
Find the slope-intercept form of the equation of the line that goes through $(2,1)$ and is perpendicular to the line $5x - 7y = 35$.

\vskip 3.25in
\item
Graph the function. Label your endpoints with their coordinates.
\begin{equation*}
f(x) = 
\begin{cases}
|x|    &\text{for } x < 2 \\
4 - x &\text{for } x \geq 2 
\end{cases}
\end{equation*}

\eject
\item
Identify the vertex AND $x$-intercept(s). $$y = 2x^2 - 8x + 1$$

\vskip 3in
\item
Find the partial fraction decomposition. $$\dfrac{6x - 6}{x^2 - 4x - 5}$$

\eject
\item
Solve for $x$. Check your solution(s). $$\log_{3}(x) + \log_{3}(x - 6) = 3$$

\vskip 3.5in
\item
Solve $2^x = 7^{x - 3}$. Give an exact solution.

\eject
\item
Evaluate exactly.
\begin{enumerate}
\vskip .05in
\item
$\sin 420 \degree$

\vskip .6in
\item
$\cos \left(- \dfrac{3 \pi}{4} \right)$

\vskip .6in
\item
$\cot(-390 \degree)$

\vskip .6in
\item
$\sec \left( \dfrac{5 \pi}{6} \right)$
\end{enumerate}

\vskip .6in
\item
Given $\alpha = 45 \degree$, $b = 42$, and $a = 37$, determine (and state) the number of triangles and solve \underline{one} existing triangle.

\eject
\item
Solve the system
\begin{align*}
&y = 2x^2 - 2 \\
&x + y = 4
\end{align*}
algebraically. Then graph both equations on the same coordinate system to support your solution.

\vskip 2.75in
\item
Use the identity $$\sin(\alpha - \beta) = \sin{\alpha}\cos{\beta} - \cos{\alpha}\sin{\beta}$$ to find the exact value of $$\sin \left( \dfrac{7 \pi}{12} \right).$$

\eject
\item
In this problem, clearly label the exact values of the coordinates of the $x$-axis and $y$-axis for each part (you will receive no credit if this is not done). Graph $$f(x) = 3 \sin(2x + \pi / 2)$$ using the following steps.
\begin{enumerate}
\item
Sketch at least one cycle of $y = \sin{x}$. What is the period?
\vskip 1.5in
\item
Sketch at least one cycle of $y = \sin{2x}$. What is the period?
\vskip 1.5in
\item
Sketch at least one cycle of $y = 3 \sin(2x)$. What is the amplitude?
\vskip 1.5in
\item
Sketch at least one cycle of $y = f(x)$. What is the phase shift?
\end{enumerate}

\eject
\item
Use the identity $$\tan \dfrac{x}{2} = \dfrac{\sin{x}}{1 + \cos{x}}$$ to find the exact value of $$\tan(67.5 \degree).$$

\vskip 3in
\item
Graph $y = \cot{x}$ in the interval $[ -2 \pi , 2 \pi ]$.

\eject
\item
Solve each system by your method of choice. Determine whether each system is independent, inconsistent, or dependent.
\begin{enumerate}
\vskip .05in
\item
$3x - y = 3$

$x + 2y = 1$

\vskip 2in
\item
$6x + 2y = 3$

$y = -3x + 1$

\vskip 2in
\item
$5x - 2y = \dfrac{1}{2}$

$\dfrac{1}{5}x - \dfrac{1}{2}y = 2$
\end{enumerate}

\eject
\item
Graph the solution set to $x^2 + y^2 \leq 36$ and $y - 2x \geq 4$. 

\end{enumerate}
\end{document}
