\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amsfonts,amssymb,amsxtra}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}
\renewcommand{\theenumi}{(\alph{enumi})} 
\renewcommand{\labelenumi}{\theenumi}

\pagestyle{empty}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\textheight}{9.5in}

\newtheorem{problem}{Problem}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 1
\noindent{\large\bf MATH 141}\hfill{\large\bf Exam\#2
  (extension|var.~1).}\hfill{\large\bf Fall 2009}\hrule 

\bigskip
{\problem[15 pts] \em A rectangular area of $3200~\text{ft}^2$ is to
  be fenced off.  Two opposite sides will use fencing costing \$1 per
  foot and the remaining sides will use fencing costing \$2 per foot.
  Find the dimensions of the rectangle of least cost.}
\vspace{7.5cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (-3.5cm,0.5cm) node {Dimensions of rectangle of least cost:};
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\hrule
{\problem[15 pts] \em Grain pouring from a chute at the rate of
  $8~\text{ft}^3/\text{min}$ forms a conical pile whose height is
  always twice its radius.  How fast is the height of the pile
  increasing at the instant when the pile is $6~\text{ft}$ high?}
\vspace{8.5cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (-3.6cm,0.5cm) node {Height of pile increasing at a rate of:};
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 2
\noindent{\large\bf MATH 141}\hfill{\large\bf Exam\#2
  (extension|var.~2).}\hfill{\large\bf Fall 2009}\hrule 

\bigskip
{\problem[15 pts] \em A 17-ft ladder is leaning against a wall.  If
  the top of the ladder slips down the wall at a rate of
  $2~\text{ft}/\text{s}$, how fast will the foot be moving away from
  the wall when the top is $5~\text{ft}$ above the ground?}
\vspace{7.5cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (-3cm,0.5cm) node {Foot moving away at a rate of:};
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\hrule
{\problem[15 pts] \em A box with a square base is taller than it is
  wide.  In order to send the box through the U.S.~mail, the height of
  the box and the perimeter of the base can sum no more than
  $108~\text{in}$.  What is the maximum volume for such a box?}
\vspace{8.5cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (-1.6cm,0.5cm) node {Largest volume:};
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 3
\noindent{\large\bf MATH 141}\hfill{\large\bf Exam\#2
  (extension|var.~3).}\hfill{\large\bf Fall 2009}\hrule 

\bigskip
{\problem[15 pts] \em At noon, ship \textbf{A} is $150~\text{km}$ west
  of ship \textbf{B}.  Ship \textbf{A} is sailing east at
  $35~\text{km}/\text{h}$ and ship \textbf{B} is sailing north at
  $25~\text{km}/\text{h}$.  How fast is the distance between the ships
  changing at 4:00~PM?}
\vspace{7.5cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (-3cm,0.5cm) node {Distance changing at a rate of:};
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\hrule
{\problem[15 pts] \em A church window consisting of a rectangle topped
  by a semicircle is to have a perimeter $p$.  Find the radius of the
  semicircle if the area of the window is to be maximum.} 
\vspace{8.5cm}
\begin{flushright}
  \begin{tikzpicture}
    \draw (-1.8cm,0.5cm) node {Semicircle radius:};
    \draw (0cm,-0.2cm) rectangle (5cm,1.2cm);
  \end{tikzpicture}
\end{flushright}
\end{document}
