\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amsfonts,amssymb,amsxtra}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}
\renewcommand{\theenumi}{(\alph{enumi})} 
\renewcommand{\labelenumi}{\theenumi}

\pagestyle{empty}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\textheight}{9.5in}

\theoremstyle{definition}
\newtheorem{problem}{Problem}

\begin{document}

\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5d.}\hfill{\large\bf Fall 2017}\hfill{\large\bf Page 1/3}\hrule

\bigskip
\begin{center}
  \begin{tabular}{|ll|}
    \hline & \cr
    {\bf Name: } & \makebox[12cm]{\hrulefill}\cr & \cr
    {\bf VIP ID:} & \makebox[12cm]{\hrulefill}\cr & \cr
    \hline
  \end{tabular}
\end{center}
\begin{itemize}
\item Write your name and VIP ID in the space provided above.
\item The test has three (3) pages, including this one.
\item Credit for each problem is given in parentheses at the right of the problem number.
\item No books, notes or scratch paper may be used on this test.
\item An approved calculator may be used on this test.
\end{itemize}
\hrule

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 2
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5d.}\hfill{\large\bf Fall 2017}\hfill{\large\bf Page 2/3}\hrule

\bigskip
\begin{problem}[10 + 15 pts]
Evaluate the following integrals.
\begin{enumerate}
\item $\displaystyle{\int_{1.1}^{1.8} \frac{t^2}{e^t \ln t}\, dt} = $
\vspace{1cm}
\item $\displaystyle{\int_{10}^{118} \frac{4x^6}{(x^7+7)^{21}}\, dx = }$
\vspace{8cm}
\end{enumerate}
\end{problem}
\hrule

\begin{problem}[25 pts]
Find the average value of the function $f(x) = 30\sqrt{16-x^2}$ between $x=0$ and $x=4$.
\end{problem}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 3
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5d.}\hfill{\large\bf Fall 2017}\hfill{\large\bf Page 3/3}\hrule

\bigskip
\begin{problem}[25 pts]
For a product, the demand curve is $p=40e^{-0.008q}$ and the supply curve is $p=2\sqrt{q}+5$ for $0 \leq q \leq 500$, where $q$ is quantity and $p$ is price in dollars per unit.  Find the consumer surplus at the equilibrium (round your answer to the nearest dollar).
\vspace{10cm}
\end{problem}
\hrule

\begin{problem}[25 pts]
The marginal cost of drilling an oil well depends on the depth at which you are drilling;  drilling becomes more expensive, per meter, as you dig deeper into the earth.  The fixed costs are one million riyals, and if $x$ is the depth in meters, the marginal costs are $MC(x) = 2000 + 16x$ riyals per meter.  Find the total cost of drilling a 400 meter well.
\end{problem}

\end{document}
