\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amsfonts,amssymb,amsxtra}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}
\renewcommand{\theenumi}{(\alph{enumi})} 
\renewcommand{\labelenumi}{\theenumi}

\pagestyle{empty}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\textheight}{9.5in}

\theoremstyle{definition}
\newtheorem{problem}{Problem}

\begin{document}

\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Fall 2016}\hfill{\large\bf Page 1/3}\hrule

\bigskip
\begin{center}
  \begin{tabular}{|ll|}
    \hline & \cr
    {\bf Name: } & \makebox[12cm]{\hrulefill}\cr & \cr
    {\bf VIP ID:} & \makebox[12cm]{\hrulefill}\cr & \cr
    \hline
  \end{tabular}
\end{center}
\begin{itemize}
\item Write your name and VIP ID in the space provided above.
\item The test has three (3) pages, including this one.
\item Credit for each problem is given in parentheses at the right of the problem number.
\item No books, notes or scratch paper may be used on this test.
\item An approved calculator may be used on this test.
\end{itemize}
\hrule

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 2
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Fall 2016}\hfill{\large\bf Page 2/3}\hrule

\bigskip
\begin{problem}[10 + 15 pts]
Evaluate the following integrals.
\begin{enumerate}
\item $\displaystyle{\int_{0}^{4} \ln(y^2 + 1) \, dy} = $
\vspace{1cm}
\item $\displaystyle{\int_{10}^{103} 9xe^{x^2}\, dx = }$
\vspace{8cm}
\end{enumerate}
\end{problem}
\hrule

\begin{problem}[25 pts]
What is the average value of $f(x) = \displaystyle{\sqrt{\vphantom{\lvert} 9-x^2}}$ over the interval $0 \leq x \leq 3$?  Round your answer to two decimal places.
\end{problem}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 3
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Fall 2016}\hfill{\large\bf Page 3/3}\hrule

\bigskip
\begin{problem}[25 pts]
For a product, the demand curve is $p=53-q^2$ and the supply curve is $p=3+q^2$, where $q$ is quantity and $p$ is price in dollars per unit. Find the producer surplus when the market is in equilibrium (round your anwer to the nearest dollar).
\vspace{10cm}
\end{problem}
\hrule

\begin{problem}[25 pts]
After a foreign substance is introduced into the blood, the rate at which antibodies are made is given by
\begin{equation*}
r(t) = \frac{t}{t^2+1} \text{ thousands of antibodies per minute,}
\end{equation*}
where time $t$ is in minutes.  Assuming there are no antibodies present at time $t=0$, find the total quantity of antibodies in the blood at the end of 7 minutes.
\end{problem}

\end{document}
