\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amsfonts,amssymb,amsxtra}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}
\renewcommand{\theenumi}{(\alph{enumi})} 
\renewcommand{\labelenumi}{\theenumi}

\pagestyle{empty}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\textheight}{9.5in}

\theoremstyle{definition}
\newtheorem{problem}{Problem}

\begin{document}

\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Fall 2016}\hfill{\large\bf Page 1/3}\hrule

\bigskip
\begin{center}
  \begin{tabular}{|ll|}
    \hline & \cr
    {\bf Name: } & \makebox[12cm]{\hrulefill}\cr & \cr
    {\bf VIP ID:} & \makebox[12cm]{\hrulefill}\cr & \cr
    \hline
  \end{tabular}
\end{center}
\begin{itemize}
\item Write your name and VIP ID in the space provided above.
\item The test has three (3) pages, including this one.
\item Credit for each problem is given in parentheses at the right of the problem number.
\item No books, notes or scratch paper may be used on this test.
\item An approved calculator may be used on this test.
\end{itemize}
\hrule

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 2
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Fall 2016}\hfill{\large\bf Page 2/3}\hrule

\bigskip
\begin{problem}[10 + 15 pts]
Evaluate the following integrals.
\begin{enumerate}
\item $\displaystyle{\int_{1.1}^{1.8} e^t \ln t\, dt} = $
\vspace{1cm}
\item $\displaystyle{\int_{1}^{108} 10xe^{x^2}\, dx = }$
\vspace{8cm}
\end{enumerate}
\end{problem}
\hrule

\begin{problem}[25 pts]
Find the average value of the function $f(x) = 11+10x-x^2$ between $x=0$ and $x=3$.
\end{problem}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page 3
\noindent{\large\bf MATH 122}\hfill{\large\bf Exam \#5.}\hfill{\large\bf Fall 2016}\hfill{\large\bf Page 3/3}\hrule

\bigskip
\begin{problem}[25 pts]
For a product, the demand curve is $p=80e^{-0.008q}$ and the supply curve is $p=4\sqrt{q}+10$ for $0 \leq q \leq 500$, where $q$ is quantity and $p$ is price in dollars per unit.  Find the consumer surplus at the equilibrium (round your answer to the nearest dollar).
\vspace{10cm}
\end{problem}
\hrule

\begin{problem}[25 pts]
A forest fire covers 2002 acres at time $t=0$.  The fire is growing at a rate of $8\sqrt{t}$ acres per hour, where $t$ is in hours.  How many acres are covered 24 hours later? (round your answer to the nearest integer)
\end{problem}

\end{document}
